% ************ Acknowledgements ************
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
While there is only one person's name on the front of a thesis, in reality, it is the culmination of the hard work and dedication of many people and, as such, it is only right that a thesis should start by acknowledging the contributions and sacrifices made by others on behalf of the author.
\par
First and foremost, I must thank my supervisor Phil Mauskopf; without whose encouragement and belief in me, I simply would not have reached this stage.  Working in Phil's lab during the summers of my undergraduate degree taught me that research can be as rewarding  as it can be infuriating, however, it is ultimately addictive. 
\par
During my PhD, several others have also acted as my advisors and co-supervisors. Gao Min, Dan Reed, Simon Doyle and Peter Ade have always had a seemingly unlimited supply of time for me and for this I am exceedingly grateful.
\par
I am indebted to my collaborators from other institutes, particularly Professors Evan Parker and Terry Whall from Warwick. Their group's ability to grow the strained and highly-doped material used here not only made the detectors work but do so impressively well. They have always been on the phone and striving to push this technology as far as humanly possible.
\par
For all but the final few months of my studies, I was lucky enough to share an office and lab with Dmitry Morozov. While at times bizarre, it was a great deal of fun and, after Dmitry humming it for over four years, I don't think I will ever truly get \textit{Popcorn} by Gershon Kingsley out of my head; thanks for that!
\par 
Rob Tucker and Rashmi Sudiwala for their support with electronics, grounding issues, and answering all those questions beginning ``I've tried everything I can think of but\ldots''. Also, thanks must go to Rashmi for teaching me that there is only one way to do something: the correct way, and then you only do it once. Working with you has certainly been an experience. I am indebted to Chris Dunscombe for his support in the clean room fabricating the detectors tested here and explaining how to design photomasks that might actually be of use. Amber Hornsby for operating the FTS during most of my runs. Richard Frewin you are, I can only deduce, some kind of magic computing wizard.
\par
I have been lucky enough to spend a great deal of time---perhaps more than I should have---as a member of the Cardiff University Fencing Club and the Men's First \Rom{9}.  To all the members of the club and my teammates; the days spent training and travelling all over the country with you have been a pleasure. Abi, Amy, Chris W, Drew, Ed, Eryn, Flavia, Jack, James, Jon, Josie, Lauren, Lydia, Mark, Miguel, Pete G, Pete R, Reggie, Rosie, Sarah G, Sarah E, Steve, Tedi, Tessa, Tim, Tom, Zo\"{e}, and anyone one I have terribly, inevitably forgotten, I wish you all the best. A special mention has to go to Andy McLeod who, by some strange twist of fate, I seem to have been crossing paths with, in various walks of life, for well over a decade now. You have been an outstanding friend and I hope we continue to stumble into each other for many decades to come.
\par
To my fellow PhD students, both past and present, you have been excellent providers of weekly cake, buyers of beer, and, of course, very dear friends. Adam, Andrew, Andy, Camilo, Chris C, Chris F, Ciara, Craig, Ezzy, George F, George S, Geraint, Gwen, Ian, Jess, Kane, Laura, Mark, Mat, Matt, Olly, Olivia, Patricia, Paul, Pete, Peter, Ryan, Sam, Sarah, Scott, Scotty, Seb, Simon, Tom A, and Tom B (the other one). To all of you who have finished your PhD, wherever you may now be, you have my congratulations; to the rest of you, you can have my reassurance that the final months and weeks are most certainly an experience.
\par
To my Mum, who has supported me through so much, it is impossible to express in writing how very grateful I am for everything you have done for me. I am, however, in no doubt that you know this and, as such, I will simply say `thank you'. Thank you.
\par
Finally, and without a shadow of a doubt most importantly, to my amazing wife Sarah; you have supported me throughout the last three-and-a-half years and through everything that a PhD throws at a person. You have shown me unconditional love and patience, which must border on insanity. I consider myself immeasurably lucky to simply call you my friend, however, to call myself your husband is an honour. While this journey for me is coming to a close, I cannot wait for all the adventures we will share together.

